Supervised Learning for Psychological Attention to High School Students

### 2020-11-18 article/article.tex
[ article ] writing ideas for conclusions

The results are presented using three learning curves: the sum of local
gradients per layer at the end of each epoch, the average error energy and a
Receiver Operating Characteristic (ROC) curve, comparing the obtained results
with the real labels.
\begin{itemize}
  \item The sum of gradients per layer at the end of each epoch is an approach
  visualizing if the training algorithm is solving the optimization problem,
  since the sum of local gradients must converge to zero as each gradient
  converges to zero. It is well-known that the vanish of gradients is a
  necessary condition for optimality and the training algorithm is just an
  optimization problem minimizing the output error (cost function).
  \item The average error energy is the cost function of the optimization
  problem. Let $y_i\in\mathbb{R}^n$ be the real output of a given input pattern
  $x_i\in\mathbb{R}^m$ and let $\hat{y}_i\in\mathbb{R}^n$ be the output of the
  NN for the same input pattern. Denoting each component by superscripts, the
  average error energy $\xi_{av}$ on each epoch is then computed as
\begin{equation}
\xi_{av}=\dfrac{1}{2}\sum_{i=1}^{N}\sum_{k=1}^n\left(y^k_i-\hat{y}^k_i\right)^2,
\end{equation}
  where $N$ is the training sample size. Thus, it is clear that
  $\xi_{av}\rightarrow0$ is a good initial approach for evaluating the
  learning performance.
  \item The ROC curve is a tool that helps visualize the correct classifications
  of the learning machine by plotting the true positive rate on the vertical
  axis, and false positive rate on the horizontal axis. The Area Under the Curve
  (AUC) is an indicator of how good the data is being classified by the model,
  with higher values being better usually better.
\end{itemize}

@@

\section{Conclusions}\label{sec:conc}

>>>>

The results are presented using three learning curves: the sum of local
gradients per layer at the end of each epoch, the average error energy and a
Receiver Operating Characteristic (ROC) curve, comparing the obtained results
with the real labels.
\begin{itemize}
  \item The sum of gradients per layer at the end of each epoch is an approach
  visualizing if the training algorithm is solving the optimization problem,
  since the sum of local gradients must converge to zero as each gradient
  converges to zero. It is well-known that the vanish of gradients is a
  necessary condition for optimality and the training algorithm is just an
  optimization problem minimizing the output error (cost function).
  \item The average error energy is the cost function of the optimization
  problem. Let $y_i\in\mathbb{R}^n$ be the real output of a given input pattern
  $x_i\in\mathbb{R}^m$ and let $\hat{y}_i\in\mathbb{R}^n$ be the output of the
  NN for the same input pattern. Denoting each component by superscripts, the
  average error energy $\xi_{av}$ on each epoch is then computed as
\begin{equation}
\xi_{av}=\dfrac{1}{2}\sum_{i=1}^{N}\sum_{k=1}^n\left(y^k_i-\hat{y}^k_i\right)^2,
\end{equation}
  where $N$ is the training sample size. Thus, it is clear that
  $\xi_{av}\rightarrow0$ is a good initial approach for evaluating the
  learning performance.
  \item The ROC curve is a tool that helps visualize the correct classifications
  of the learning machine by plotting the true positive rate on the vertical
  axis, and false positive rate on the horizontal axis. The Area Under the Curve
  (AUC) is an indicator of how good the data is being classified by the model,
  with higher values being usually better.
\end{itemize}

\subsection{Sensitivity-Specificity}
The sensitivity is a ``measure of the proportion of actual positive cases that
got predicted as postive (true positive)'' and the specificity is ``measure of
proportion of actual negatives that got predicted as negatives (true negatives)
'' \parencite{sens}. This values are, hence, calculated using the formulae
\begin{align}
  \mathrm{Sensitivity}=&\dfrac{TP}{TP+FN},\quad
  \\\mathrm{Specificity} =&
  \dfrac{TN}{TN+FP},
\end{align}
where TP stands for True Postives, FN for False Negatives, TN for True Negatives
and FP for False Negatives, which are extracted from a confusion matrix.

@@

\section{Conclusions}\label{sec:conc}
The results presented gave insight on how the two classes could be separated.
The authors are keen on the idea that these shattered points could be mapped
into a more intuitive interpretation of individuals requiring psychological
attention (class 0) and others that show apparent ``normal'' conditions (class
1). Note that this is pure speculation and would need confirmation by better
qualified personnel.

As for future work, the hypothesis and results here presented could be reviewed
by an expert, since this work is preliminary and the authors are no experts in
Mental Health. Additionally, a better review of sophisticated techniques for
visualizing learning machines could be done, since the 2-dimensional embedding
of the decision function (contours) was more of an heurisitc approach proposed
by the authors and it could be somehow improved. Finally, the inclusion of more
metrics for evaluating the performance of the classifiers can be included as
well, since only the Sensitivity-Specificity was done.
